\documentclass[12pt]{exam}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Final Exam}
\author{Nate Iverson}
\course{Linear Algebra}
\classtime{12:00-12:50 pm MWF} % can ommit this line if multiple sections
\section{01} % can ommit this line if multiple sections
\term{Winter 2014}
\date{4/28/2014}

\begin{document}
\maketitle
\emph{Instructions:} Show your work for full credit. Staple this sheet to the top of your work for each problem. Make sure each part is labelled and in the same order as this sheet. Good Luck :)

\begin{enumerate}
\item ( 4 points each ) Rank Nullity Theorem
\begin{enumerate}
\item For a linear transformation $T:V \to W$ state the rank-nullity theorem.
\item If $T:\mathbb{R}^7 \to \mathbb{R}^3$ is a linear transformation that has $\dim \text{null}(T)=5$, what is  $\text{rank}(T)$ ?
\item Is it possible for a linear transformation  $T:\mathbb{R}^7 \to \mathbb{R}^3$ to be one-to-one?
\item If $T:V\to W$ is a linear transformation with $\text{rank}(T)=4$ and $\dim \text{null}(T)=5$ find $\dim(V)$.
\end{enumerate}
\item ( 6 points each) $T:\mathbb{R}^2\to \mathbb{R}^4$ is defined by
$T\begin{pmatrix}a\\b\end{pmatrix}=
\begin{pmatrix} 
a-b\\
b-a\\
2a\\
a-3b\\
\end{pmatrix}$
\begin{enumerate}
\item Show $T$ is a linear transformation.
\item Find the standard matrix for $T$
\item Is $T$ one-to-one? (Why?)
\item Is $T$ onto? (Why?)
\end{enumerate}
\item ( 60 points ) Diagonalization
\begin{enumerate}
\item $A=\left(\begin{array}{rr}
-1 & 4 \\ 9 & -1
\end{array}\right)$
\begin{enumerate}
\item Find all the eigenvalues of $A$.

\item For each eigenvalue  find a basis for the corresponding eigenspace.  

\item Is $A$ diagonizable? If yes, find diagonal matrix $D$, invertible matrix $P$ and inverse $P^{-1}$ such that $A=PDP^{-1}$. If no, state why not.

\end{enumerate}
\item $B=\left(\begin{array}{rrr}
   3  & 1 & -1\\
  -1  & 1 &  1\\
   0  & 0 &  2
\end{array}\right)$
\begin{enumerate}
\item Find all the eigenvalues of $B$.

\item For each eigenvalue  find a basis for the corresponding eigenspace.  

\item Is $B$ diagonizable? If yes find diagonal matrix $D$, invertible matrix $P$ and inverse $P^{-1}$ such that $B=PDP^{-1}$. If no, state why not.

\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{document}
